Large-scale harmonic patterns clustering

### 2010-03-11 Paper/Paper.tex
improvements

\section{Previous Work}\label{sec:prevwork}
The idea is closely related to the \textit{Shingles} described by
Slaney and Casey \cite{Casey2006,Casey2007,Casey2008}.

LSH: \cite{Datar2004}, LSH implementation: \cite{E2LSH}.
The E$^2$LSH packages can efficiently handle about $50$K or $100$K
vectors of size $200$. Even with a better implementation, the LSH
model still has some scaling problem. A large portion of the data
must be known to decide how many projections to use, and what guarantee
of finding the nearest neighbor it can provides. Also, we could fix the
number of projections and consider as clusters all the elements that
fall into the same bin. However, this does not give us a centroid, a
typical pattern representing that cluster.

Barrington et al. recently studied music texture using a set of ordered
MFCC vectors \cite{Barrington2009a}. This could be seen as complementary
to our work. Chromas capture the harmonic information and some of the
rythm while the MFCC are great timbral features.

>>>>

\section{Previous Work}\label{sec:prevwork}
Our work can be seen as an extension of the \textit{Shingles} idea
described by Casey and Slaney \cite{Casey2006,Casey2007,Casey2008}.
The two main differences are the clustering framework and the use of
beats and bars to select the position of the \textit{Shingles}.

Casey and Slaney \cite{Casey2006} use LSH \cite{Datar2004} to perform
fast approximate nearest neighbor search. Their implementation is E$^2$LSH
\cite{E2LSH}. This package can efficiently handle about $50$K or $100$K
vectors of size $200$. Even with a better implementation, the LSH
model still has some scaling problem. A large portion of the data
must be known to decide how many projections to use, and what guarantee
of finding the nearest neighbor it can provides. Also, we could fix the
number of projections and consider as clusters all the elements that
fall into the same bin. However, this does not give us a centroid, a
typical pattern representing that cluster.

Regarding similar representations of music,
Barrington et al. recently studied music texture using a set of ordered
MFCC vectors \cite{Barrington2009a}. This could be seen as complementary
to our work. Chromas capture the harmonic information and some of the
rythm while the MFCC are great timbral features.
